\documentclass{./worksheet}
\usepackage[colorlinks=true, urlcolor=blue]{hyperref}

\mytitle{Introduction to C}

\begin{document}

This worksheet will give you some practice using the C programming language. Make sure to refer to the slides if you are forgetting
any of the syntax or the library functions. You can also raise your hand and ask for help if you are stuck!
\begin{enumerate}

\item Write a simple C program that creates two integers and computes its sum.
Then print a message back to the screen, in the format ``\verb|<int1>| plus \verb|<int2>| equals \verb|<sum>|".

\textbf{Challenge}: have the program read the two integers from the user instead of hardcoding them.
You can use the following resource to help you \url{https://www.w3schools.com/c/c_user_input.php}

\item Save your program in the file \verb|intro_c.c|. What is the command to compile your
program into an executable named \verb|intro_c|?
\vspace{0.5in}

\item In the same program or a new one. Define a struct type that represents the current
time. It should have fields for the hour, minute, and second. Create a variable
of this struct to store the current time (just enter it manually).

\textbf{Challenge}: have
the variable store the current time automatically using the \verb|time()| function.
You can use the following resource to help you \url{https://www.w3schools.com/c/c_date_time.php}

\item Write a function that takes in this time struct as an argument and
prints it to the screen in the format ``\verb|HH:MM:SS|".

\item Create an array of time structs set to random times.
Create a for loop to iterate through the array and print each time.

\item Create a while loop in main that updates the struct every second and prints the new time.
Remember there cannot be more than 60 seconds ;).
(hint: you'll need to modify the struct and use the \verb|sleep()| function)

\item Will your program run forever? Discuss with your partner and write down
your answer, then press \verb|Ctrl+C| while in your terminal to stop it.
\vspace{1in}

\item Modify your while loop so that it stops when a minute has passed.

\textbf{Challenge}: Replace the while loop logic with a for loop instead.

\end{enumerate}


\end{document}
